### 2008-12-19 talk/ecoop2009/rainbow.tex
kill a now-unnecessary section

\section{Promotion}

@@

Virtual structures still avoid the run-time allocation of most
short-lived objects, even in non-trivial situations.  The following
example shows a typical case.  XXX use TLC example

The PyPy Python interpreter
implements application-level integers as boxes – instances of a
\texttt{W\_IntObject} class with a single \texttt{intval} field.  Here is the
addition of two integers:

>>>>

\section{Promotion}
\label{sec:promotion}

@@

Virtual structures still avoid the run-time allocation of most
short-lived objects, even in non-trivial situations.  The following
example shows a typical case.  The TLC interpreter implements application-level
integers as boxes – instances of an \texttt{IntObject} class with a single
field.
